A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-02 main.tex
Wrote on Q-% rule.

Third, we also need type equivalence rules in \LMD as a dependent type system.

@@

>>>>

Third, we also need type equivalence rules in \LMD as a dependent type system.
Although there are new primitives relating to stages which aren't in \LLF,
we can design all rules except \QPercent\ easily.
\red{design?}
\red{この段落が短い。後ろとくっつけてもいいが、段落の趣旨がボケる。}

@@

The biggest problem in extension is handling the CSP symbol $\%_\alpha$ in \LMD.
The equvalence simple rule to handle CSP is \QCsp.
\begin{center}
	\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau@{A\alpha}}{\QCsp}
\end{center}
However, this rule isn't enough when the parameters of dependent types are cross-staed.
We will discuss on this problem in later section and solve this problem with the new rule \QPercent.
\begin{center}
	\infrule{\G\V M:\tau@{A\alpha} \andalso \G\V M:\tau@A}{\G\V\%_\alpha M \E M : \tau@{A\alpha}}{\QPercent}
\end{center}
\red{この段落でQ-Cspの持つ問題点を指摘すべきか? ただ、ここでmulmatの例を使うと3章と被る。}
